### 2020-05-05 main.Rmd
added flowchart on the Rmd

```{r, effectorcollection, fig.cap="Workflow diagram for collection of effector sequences from the PHI-Base database annotation and cross reference to UniProt"}
knitr::include_graphics(
  "figures/effectorsequence_collection.png",
                        )
```

>>>>

```{r, effectorcollection, out.width='50%', fig.align='center', fig.cap="Workflow diagram for collection of effector sequences from the PHI-Base database annotation and cross reference to UniProt"}
knitr::include_graphics(
  "figures/flowchart_effectorsequence_collection.pdf",
)
```

```{r, noneffectorcollection, fig.cap="Workflow diagram for collection of secreted non-effector sequences from Ensembl Bacteria, Fungi, and Protists"}
knitr::include_graphics(
  "figures/flowchart_secreted_noneffectorsequence_collection.pdf",
)
```
